IGAS Project

### 2024-04-09 Sections/IGAS.qmd
generate md of IGAS

---
title: IGAS Project
subtitle: An instance-based model account of the benefits of varied practice in visuomotor skill
date: last-modified
#page-layout: full
code-fold: true
code-tools: true
toc: true
toc-location: body
toc-title: Contents
execute: 
  warning: false
  eval: true
editor: 
  markdown: 
    wrap: 72
---

>>>>

---
title: IGAS Project
subtitle: An instance-based model account of the benefits of varied practice in visuomotor skill
date: last-modified
#page-layout: full
code-fold: true
code-tools: true
toc: true
toc-location: body
toc-title: Contents
format:
  html: default
  hugo-md:
    echo: false
    include: false
    html-math-method: mathjax
    output-file: igas_hugo.md
execute: 
  warning: false
  eval: true
editor: 
  markdown: 
    wrap: 72
---
